Size, Shape and Functionality Dependence of Solute Transport Mechanisms in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-01-30 Ben_Manuscripts/transport/Outline.tex
Added test

\title{The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  \subsubsection*{Modeling subdiffusion}\label{method:CTRW}

@@

  \subsection{Simulated Predictions}\label{section:D_macro}

  We extracted values of $\sigma$, $\alpha$ and $H$ for each solute and then
  simulated 10000 solutes trajectories as described in the Methods. The results
  are presented in Table~\ref{table:simulations}.

  % Add MD calculated MSD to this?
  \begin{table}[h]
  \centering
  \begin{tabular}{ccccc}
  \toprule
  System & $\sigma$ ($nm$) & $\alpha$ & $H$ & Simulated MSD ($nm^2$)\\
  \midrule
  Methanol & 0.46 & 0.85 & 0.40 & 55.06 [49.26, 60.58] \\
  Urea & 0.33 & 0.64 & 0.40 & 15.64 [14.08, 17.32] \\
  Ethylene Glycol & 0.35 & 0.64 & 0.36 & 6.30 [5.69, 6.93] \\
  Acetic Acid & 0.28 & 0.51 & 0.43 & 4.11 [3.66, 4.65] \\
  Mercaptoethanol & 0.32 & 0.58 & 0.37 & 2.54 [2.16, 2.93] \\
  Propylene Glycol & 0.26 & 0.50 & 0.43 & 1.94 [1.70, 2.17] \\
  Ethanol & 0.32 & 0.55 & 0.26 & 1.29 [1.14, 1.43] \\
  Propanol & 0.25 & 0.41 & 0.39 & 1.13 [1.01, 1.27] \\
  Glycerol & 0.22 & 0.46 & 0.37 & 1.09 [0.98, 1.20] \\
  Ethyl Acetate & 0.21 & 0.42 & 0.37 & 0.82 [0.74, 0.91] \\
  Acetone & 0.23 & 0.44 & 0.34 & 0.80 [0.70, 0.88] \\
  Dimethyl Sulfoxide & 0.25 & 0.47 & 0.29 & 0.74 [0.65, 0.82] \\
  Tetrose & 0.22 & 0.43 & 0.20 & 0.68 [0.61, 0.75] \\
  Acetamide & 0.27 & 0.52 & 0.21 & 0.56 [0.51, 0.64] \\
  2,3-Dimercapto-1-propanol & 0.20 & 0.38 & 0.37 & 0.53 [0.47, 0.58] \\
  Butanol & 0.19 & 0.41 & 0.33 & 0.42 [0.36, 0.49] \\
  Propylene Carbonate & 0.19 & 0.38 & 0.29 & 0.30 [0.26, 0.34] \\
  Tetrahydrofuran & 0.25 & 0.40 & 0.24 & 0.29 [0.25, 0.34] \\
  Dimethyl Formamide & 0.20 & 0.39 & 0.27 & 0.27 [0.24, 0.31] \\
  Ribose & 0.21 & 0.43 & 0.23 & 0.27 [0.24, 0.31] \\
  \bottomrule
  \end{tabular}
  \caption{We calculated values $\sigma$, $\alpha$ and $H$ from MD simulation
  trajectories and then computed the average ensemble-averaged MSD of 10000 
  simulated trajectories.}\label{table:simulations}
  \end{table}

  It most cases, it is easy to relate $\sigma$, $\alpha$ and $H$ to the simulated
  simulated MSD values presented in Table~\ref{table:simulations}. 
  \begin{itemize}
  	\item Higher values of $\sigma$ indicate larger average hop lengths.
  	\item Higher values of $\alpha$ mean that there will be less sampling of 
  	long dwell times.
  	\item Values of $H$ near the Brownian limit of 0.5, indicate a lower degree
  	of anti-correlation.
  	\item All of which contribute to an overall increase in the simulated MSD
  \end{itemize}

  Polar molecules generally exhibit a hop diffusion mechanism. 
  \begin{itemize}
	\item Each trajectory is characterized by a power law distribution of
	dwell times between hops of random lengths from a Gaussian distribution.
  \end{itemize}

>>>>

%BJC: potential titles (uncommented is current favorite)
%\title{The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\title{Size, Shape and Functionality Dependence of Solute Transport Mechanisms in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  \subsubsection*{Modeling subdiffusion}\label{method:model_sFBM}

@@

  \subsection{Governing Mechanisms}\label{section:mechanism_overview}

  % BJC: seems right to summarize overarching mechanisms observed first
  The mechanisms which govern transport of small polar solutes in this 
  system can be broadly described based a solute's size, shape, and polarity.
  \begin{itemize}
    \item In general, solutes can move fastest in the pore center, where
    there is comparatively little resistance to diffusion. 
  	\item The well-established trend of decreasing solute mobility with 
  	size is not defied here, however we observe small solutes with lower-than-expected
  	MSDs because they spend time trapped between monomer head groups.
  	\item Additionally, planar molecules are prone to exhibiting similar
  	trapping behavior, even for large molecules whose similar sized, but flexible
  	counterparts exhibit faster diffusion.  %BJC: this is unproven
  	\item The polarity of solutes also influences a solute's ability to stay in
  	the pore center. Highly polar molecules tend to spend more time in the pore center,
  	while those with hydrophobic character tend to spend more time in the head group
  	region.
  	\item Finally, the ability to hydrogen bond offers a second trapping mechanism. 
  	Solutes that are hydrogen bond donors can donate hydrogen atoms to
  	any of the 5 oxygen atoms located on the monomer head groups. Increasing the 
  	number of hydrogen bond donating groups increases the solute's polarity causing
  	solutes to spend more time in the pore centers, but the effect can be countered
  	by excessive trapping if there many hydrogen bonds are being formed.
  	\item Overall solutes exhibit some degree of trapping, by one or a combination of the above
  	mechanisms, with anticorrelated hops between each period of immobility due to 
  	obstructions.
  \end{itemize}

  \end{itemize}

  We will explore these factors in greater detail in the context of 
  specific groups of molecules in the discussion that follows.

  \subsection{MSD Predictions}\label{section:msd_predictions}

  %BJC: focus on MD MSD results
  \noindent We calculated the MSD of each solute in the set over the course of 1$\mu$s MD simulations.  %BJC: type of MSD TBD 
  \begin{itemize}
	\item We extracted values of $\sigma$, $\alpha$ and $H$ for each solute
	and then simulated 10000 sFBM trajectories of the same length as our MD
	simulations, as described in Section~\ref{section:model_sFBM} of the Methods.
	\item The final MSDs of the sFBM trajectories are compared to those 
	calculated directly from MD simulations in Figure~\ref{fig:all_msds}. 
	\item The three sFBM parameters, calculated based on MD solute trajectories
	are presented in Table~\ref{table:simulations}.
	\item We would like to emphasize that we rely on the MD MSD values in order to
	define trends in the total MSD, while the sFBM trajectories and parameter 
	values allow us to speculate as to the reasons for the observed trends. 
	\item There is a non-negligible amount of error in the calculation of 
	each parameter which prevents us from reliably portraying our sFBM MSDs as
	reduced	uncertainty MD MSDs.
  \end{itemize}

  Our simulated sFBM MSDs qualitatively reproduce the MD trends.
  \begin{itemize}
    \item sFBM generally lower
    \item There are a few noticeable discrepancies.
    \item We will discuss reasons for these as we proceed with the discussion.
  \end{itemize}

  \begin{figure}
  \centering
  \includegraphics[width=\textwidth]{all_emsds.pdf}
  \caption{}\label{fig:all_msds}
  \end{figure}

  % Add MD calculated MSD to this?
  \begin{table}[h]
  \centering
  \begin{tabular}{cccc}
  \toprule
  System & $\sigma$ ($nm$) & $\alpha$ & $H$ \\
  \midrule
  Methanol & 0.46 & 0.85 & 0.40 \\
  Urea & 0.33 & 0.64 & 0.40 \\
  Ethylene Glycol & 0.35 & 0.64 & 0.36 \\
  Acetic Acid & 0.28 & 0.51 & 0.44 \\
  Mercaptoethanol & 0.30 & 0.54 & 0.26 \\
  Ethanol & 0.32 & 0.55 & 0.25 \\
  Propylene Glycol & 0.26 & 0.48 & 0.35 \\
  Glycerol & 0.23 & 0.46 & 0.37 \\
  Acetamide & 0.28 & 0.52 & 0.26 \\
  Propanol & 0.25 & 0.41 & 0.35 \\
  Acetone & 0.23 & 0.44 & 0.34 \\
  Ethyl Acetate & 0.21 & 0.41 & 0.37 \\
  Dimethyl Sulfoxide & 0.26 & 0.48 & 0.26 \\
  Tetrose & 0.24 & 0.43 & 0.30 \\
  Butanol & 0.19 & 0.41 & 0.33 \\
  Dimethyl Formamide & 0.20 & 0.39 & 0.32 \\
  2,3-Dimercapto-1-propanol & 0.20 & 0.37 & 0.35 \\
  Ribose & 0.20 & 0.40 & 0.27 \\
  Propylene Carbonate & 0.19 & 0.38 & 0.29 \\
  Tetrahydrofuran & 0.24 & 0.39 & 0.16 \\
  \bottomrule
  \end{tabular}
  \caption{We calculated values $\sigma$, $\alpha$ and $H$ from MD simulation
  trajectories and then computed the average ensemble-averaged MSD of 10000 
  simulated trajectories.}\label{table:simulations}
  \end{table}

  It most cases, it is easy to relate $\sigma$, $\alpha$ and $H$ to the
  simulated MSD values presented in Table~\ref{table:simulations}. 
  \begin{itemize}
  	\item Higher values of $\sigma$ indicate larger average hop lengths.
  	\item Higher values of $\alpha$ mean that there will be less sampling of 
  	long dwell times.
  	\item Values of $H$ near the Brownian limit of 0.5, indicate a lower degree
  	of anti-correlation.
  	\item All of which contribute to an overall increase in the simulated MSD
  \end{itemize}
